\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{letter}{%
    Editor-in-Chief\\
    Natural Hazards and Earth System Sciences\\
    Copernicus Publications / European Geosciences Union
}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled \textbf{``Multi-Temporal Satellite-Based Flood Risk Assessment for 125 Municipalities in Antioquia, Colombia: Integrating Sentinel-1 SAR, JRC Water Dynamics, and Ensemble Machine Learning (2015--2025)''} for consideration for publication in \textit{Natural Hazards and Earth System Sciences}.

This study addresses a critical gap in the application of satellite remote sensing to local-scale disaster risk management in tropical developing countries. While satellite-based flood monitoring has advanced significantly at continental and global scales, most existing products lack the administrative alignment needed for municipal land-use planning---the scale at which flood risk management is operationalized in countries like Colombia.

Our key contributions are:

\begin{enumerate}
    \item A comprehensive, reproducible framework that integrates 11 years of Sentinel-1 SAR data, JRC Global Surface Water dynamics, and ensemble machine learning (Random Forest, XGBoost, LightGBM) within Google Earth Engine for municipal-scale flood risk assessment.

    \item Application to all 125 municipalities of Antioquia, Colombia's most populous department and one of its most flood-affected, producing the first department-wide flood frequency product at 10\,m resolution and population exposure estimates for each municipality.

    \item Demonstration that the framework is fully based on open-access satellite data and cloud computing, enabling replication across other departments and tropical developing countries without requiring local computational infrastructure.
\end{enumerate}

The manuscript has not been previously published and is not under consideration elsewhere. All authors have approved the manuscript and agree with its submission to NHESS. We believe it aligns well with the journal's scope of natural hazard assessment, risk analysis, and decision support using earth observation.

We declare no competing interests. The complete source code and GEE scripts will be made publicly available upon acceptance.

\closing{Sincerely,}

\vspace{-1cm}

Cristian Espinal Maya\\
School of Applied Sciences and Engineering\\
Universidad EAFIT, Medell\'in, Colombia\\
\texttt{cespinalm@eafit.edu.co}

\end{letter}
\end{document}
